Manuscript title here

### 2021-10-13 doc/ms/ms.Rmd
added text and rearranging figures to main text.

---
title: "Manuscript title here"
author: 
- name: James R Junker
  affiliation: Dept. of Ecology, Montana State University, Bozeman, MT USA
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \usepackage{indentfirst}
- \linenumbers
indent: true
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---

```{r import general objects, echo=FALSE, message=FALSE, warning=FALSE}

source("./packages.R")
drake::loadd(temperature_stats)
n_boot = temperature_stats[['n_boot']]

@@

Energy fluxes through invertebrate food webs restructured in response to temperature. Specifically, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average. Additionally, energy fluxes of warmer streams were unequally skewed towards small-bodied, high-turnover populations *within* the community, suggesting higher temperatures restructured energy fluxes in both an absolute and relative sense/both across and within communities.

@@

<!--- warming and effects in food webs --->
\setlength\parindent{24pt}
Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
[@walther2002]. Temperature's effect on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges [][] and subsequent changes to local and
regional communities [], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001]. While a growing body of theoretical and
empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [@oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017],
especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010]. Yet, identifying general effects of temperature is a necessary step
towards understanding how future warming may alter the functioning of ecosystems and the services they provide.\par

<!--- Speeding up of food web: Species levels--->
\setlength\parindent{24pt}
Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012]. The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distributions among species and trophic levels [@may1972; @mccann1998; @barnes2018]. Direct changes through species richness effects [@gibert2019]. Indirect through the distribution of consumer and prey species and it effects on the acquisition and allocation of resources among species [@zhang2017] --macroecology of food web dynamics and stability are controlled by the .\par

\setlength\parindent{24pt}
Temperature can directly alter the distribution of species interactions by asymmetric responses in organismal traits among species [e.g., attack rate, handling time, growth rates,
etc.; @dell2014].

@@

Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C). Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
[@ogorman2012; @hood2018]. Consumers rely largely on autochthonous resource [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020], as such, we predicted total annual OM fluxes to consumers to scale with among stream patterns in primary production and consumer energy demand, and therefore, increase with temperature across streams. We, further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities. The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size. Further, we predict increasing temperatures

# Methods

@@

Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 500). For taxa which exhibit synchronous growth
and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty
using a bootstrap technique similar to that described in Benke and Huryn [-@benke2017]. Individual Lengths were converted to mg AFDM using published length-mass regression cited
above and size-frequency histograms were visually inspected for directional changes in body size through time. For each date, size-frequency distributions were resampled with
replacement (*n* = 500) and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of
empirical growth data against body size and temperature within each stream. To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled
measured growth rates, in addition to abundance and size distributions from individual samples. For each iteration (*n* = 1000), size-specific growth rates were multiplied by mean
interval biomass for each size class and the number of days between sample dates to estimate size class-specific production. For each interval, size classes were summed for each
taxon to calculate total population-level production. Intervals were summed to estimate annual secondary production.

@@

**Come back and confirm this section** Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
= 3--5) to ensure samples contained enough material for quantification. We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut content
slides. Briefly, we removed the foregut from each individual or collection of individuals and sonicated gut contents in water for 30 seconds. Gut content slurries were filtered
onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a
microscope slide, cleared with Type B immersion old, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
using image analysis software [@schindelin2012]. We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
plants (bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.

| To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, is a multinomial vector,$\overrightarrow{y_i}$, of
$$\overrightarrow{y_i} \sim Multinomial(\overrightarrow{p_i}, n_i)$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value. **add in
site-level model parameter and model fitting language** . Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing
values.

| From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [*PS*; @whittaker1952] among modeled diet estimates (proportional similarity estimates from empirical diets give similar results to modeled estimates; Supporting Materials). Proportional similarities were calculated as:

@@

where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution. To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [i.e., feasible set; @haegeman2008;], given the number of species and the relative distribution of energy fluxes within a community. The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings). Therefore, we chose to permute a portion of each stream community's feasible set by randomly ordering species and calculating the skewness in the cumulative distribution of annual OM fluxes 100,000 times. The number of random orderings was chosen as a balance between characterizing the relative distribution of skewness values within each feasible set and computational and time constrains. This permuted set allowed us to calculate the likelihood of observing the empirical skewness, $Sk_{flux}$, in each stream. Further, we estimated the

@@

@@

Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1a). For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively). Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblages within streams. Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.

@@

The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively. Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C. In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature. Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3).

The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure 5). Skew towards larger body sizes was negatively associated with stream temperature. The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` -- `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C increase. The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero (Figure SXa), but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure 5a). Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature. The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 5b).

@@

# Discussion

@@

[@diaz2021] SAD are more uneven than their statistical background

@@

Jeff Wesner and Abe Kanz for code sharing and discussions on modeling diet proportions.

>>>>

---
title: "Manuscript title here"
author: 
- name: James R. Junker^[Dept. of Ecology, Montana State University, Bozeman, MT USA]
- name: Wyatt F. Cross
- name: James M. Hood
- name: Jonathan P. Benstead
- name: Alex D. Huryn
- name: Daniel Nelson
- name: Jon S. Olafsson
- name: Gisli M. Gislason
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \usepackage{indentfirst}
- \linenumbers
indent: true
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---

```{r import general objects, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("./packages.R")
library(knitr)

drake::loadd(temperature_stats)
n_boot = temperature_stats[['n_boot']]

@@

Energy fluxes through invertebrate food webs restructured in response to temperature. Specifically, communities in warmer streams were composed of smaller-bodied and higher-turnover populations on average. Additionally, energy fluxes of warmer streams were unequally skewed towards small-bodied, high-turnover populations *within* the community, suggesting higher temperatures restructured energy fluxes in both an absolute and relative sense across and within communities.

@@

<!--- warming and effects in food webs --->
Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
[@walther2002]. Temperature's effect on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges and subsequent changes to local and regional communities [@root2003], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001]. While a growing body of theoretical and
empirical study has enhanced our knowledge of temperature-mediated changes to ecosystems [\ e.g., @oconnor2009], general patterns are uncertain and empirical studies often idiosyncratic [@zhang2017; @nelson2017], especially at higher levels of organizations such as communities and food webs [@walther2002; @woodward2010]. Yet, identifying general effects of temperature is a necessary step towards understanding how future warming may alter the functioning of ecosystems and the services they provide.

<!--- Speeding up of food web: Species levels--->
Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the network of interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012]. The signature of temperature on the stability and dynamics of food webs is present across global climate gradients [@baiser2019] where its direct and indirect effects alter the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019] and the acquisition and allocation of resources among species [@zhang2017]. Importantly,  --macroecology of food web dynamics and stability are controlled by the

Temperature effects individuals by altering rates of metabolism [@gillooly2001, @brown2004] and biological activity among species [e.g., attack rate, handling time, growth rates,
etc.; @dell2014].

@@

Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5 - 28$^\circ$C). Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
[@ogorman2012; @hood2018]. Consumers rely largely on autochthonous resources [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020]. As such, we predicted total annual OM fluxes to consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams. We, further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities. The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size. 
# Methods

@@

Variability in growth rates was estimated by bootstrapping through repeated resampling of individual lengths with replacement (*n* = 1000). For taxa which exhibit synchronous growth
and development (e.g., Simuliidae spp., some Chironomidae spp., etc.), we examined temporal changes in length-frequency distributions and calculated growth rates and uncertainty
using a bootstrap technique similar to that described in Benke and Huryn [-@benke2017]. Individual Lengths were converted to mg AFDM using published length-mass regression cited
above and size-frequency histograms were visually inspected for directional changes in body size through time. For each date, size-frequency distributions were resampled with
replacement (*n* = 1000) and growth rates estimated from equation 1. We prevented the calculation of negative growth rates by requiring $W_{t + \Delta t}$ \> $W_t$. To estimate
growth rates of taxa for which growth could not be estimated empirically, we developed stream-specific growth rate models by constructing multivariate linear regressions of
empirical growth data against body size and temperature within each stream. To estimate uncertainty in production of each taxon, we used a bootstrapping technique that resampled
measured growth rates, in addition to abundance and size distributions from individual samples. For each iteration (*n* = 1000), size-specific growth rates were multiplied by mean
interval biomass for each size class and the number of days between sample dates to estimate size class-specific production. For each interval, size classes were summed for each
taxon to calculate total population-level production. Intervals were summed to estimate annual secondary production.

@@

**Come back and confirm this section** Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
= 3--5) to ensure samples contained enough material for quantification. We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut content
slides. Briefly, we removed the foregut from each individual or collection of individuals and sonicated gut contents in water for 30 seconds. Gut content slurries were filtered
onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a
microscope slide, cleared with Type B immersion old, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
using image analysis software [@schindelin2012]. We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
plants (e.g., bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.

To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, in stream, *j*, is a multinomial vector,$\overrightarrow{y_{ij}}$, of
$$\overrightarrow{y_{ij}} \sim Multinomial(\overrightarrow{p_{ij}}, n_{ij})$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value. **add in
site-level model parameter and model fitting language** . Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing
values.

From modeled diet compositions, we estimated trophic redundancy within and across stream food webs by calculating proportional similarities [*PS*; @whittaker1952] among modeled diet estimates. Proportional similarities were calculated as:

@@

where, $f_{Qx}$, is the cumulative flux at some quantile, $Qx$, of the community trait distribution. To determine if this outcome was due to random ordering, we first had to account for statistical constraints that restrict the range of possible outcomes [\ i.e., feasible set, @haegeman2008; @diaz], given the number of species and the relative distribution of energy fluxes within a community. The number of unique orderings of species increases to computationally intractable numbers very quickly (e.g., $S!$, 10 species ~3.6e^6^ unique orderings). Therefore, we chose to permute a portion of each stream community's feasible set by randomly ordering species and calculating the skewness in the cumulative distribution of annual OM fluxes 100,000 times. The number of random orderings was chosen as a balance between characterizing the relative distribution of skewness values within each feasible set and computational and time constrains. This permuted set allowed us to calculate the probability of observing the empirical skewness, $Sk_{flux}$, in each stream compared to a random ordering given the distribution of relative energy flux.

### Speed of seasonal energy flux

Lastly, to  we quantified the cumulative

@@

```{r GINI table, echo = FALSE, warning=FALSE, message=FALSE}
drake::loadd(gini_analysis)
tab1_caption = "Table 1. Evenness of energy fluxes among consumers within a stream community measured by the Gini index, both raw (\\'non-normalized\\') and \\'normalized\\' for consumer richness"
gini_analysis[["stream_gini_summary"]] %>% 
   dplyr::mutate(across(where(is.numeric),.fns = ~signif(.,2))) %>% 
   dplyr::mutate("Non-normalized Gini" = paste0(`Non-normalized Gini_mean`," ( ",`Non-normalized Gini_quant2.5`," - ", `Non-normalized Gini_quant97.5`," )"),
                 "Normalized Gini" = paste0(`Normalized Gini_mean`," ( ", `Normalized Gini_quant2.5`," - ", `Normalized Gini_quant97.5`," )")) %>% select(site, `Non-normalized Gini`,`Normalized Gini`) %>%
   dplyr::mutate(site = factor(site, levels = names(stream_order_list))) %>%
   knitr::kable(align = "lrr", caption = tab1_caption)

@@

Variation in the relative distribution of OM fluxes among consumers corresponded to different patterns of dominance across streams (Figure 1). For example, in an absolute sense, ~85% of total flux was contributed by `r n_dom_min$n_dom` to `r n_dom_max$n_dom` species (`r round(n_dom_min$dom_flux,2)`% to `r round(n_dom_max$dom_flux,2)`% of flux, respectively). Relatively, this flux was attributed by `r round(perc_dom_min$dom_spp*100,0)`% to `r round(perc_dom_max$dom_spp*100,0)`% of the species assemblages within streams. Differences in dominance were unrelated to temperature, however, species dominance in relation to population traits exhibited important differences along the temperature gradient.

```{r figure 1., echo = FALSE, warning = FALSE, message = FALSE, fig.width=5, fig.height=5, dpi = 450}
drake::loadd(annual_spp_flux_fig)
annual_spp_flux_fig
```

@@

The fluxes of OM were distributed differently across body sizes and turnover rates (*P:B*) among and within streams. Across streams, mean body size of taxa ranged from `r m_summ %>% slice_min(M_mg_ind_mean) %>% select(M_mg_ind_mean) %>% round(2)` to `r m_summ %>% slice_max(M_mg_ind_mean) %>% select(M_mg_ind_mean)%>% round(2)` mg ind^1^ and mean annual P:B ranged from `r pb_summ %>% slice_min(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` to `r pb_summ %>% slice_max(pb_y_mean) %>% select(pb_y_mean)%>% round(2)` (Figure 2). Both, *M* and *P:B* showed associations with mean annual stream temperature that were negative and positive, respectively. Generally, mean *M* of the community decreased `r M_temp_coef_mean`% (95% PI, `r M_temp_coef_quant2.5`% -- `r M_temp_coef_quant97.5`%) for each increase in 1$^\circ$C. In contrast, mean population *P:B* of the community increased `r pb_temp_coef_mean`% (95% PI, `r pb_temp_coef_quant2.5`% -- `r pb_temp_coef_quant97.5`%) for each 1$^\circ$C in mean annual stream temperature. Energy fluxes within consumer communities were skewed towards larger body sizes (positive skew), towards smaller body sizes (negative skew), or neutrally in regards to body size  among streams, with skew estimates with body size (*M*) ranging from `r m_skew_summ %>% slice_min(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean)%>% round(2)` to `r m_skew_summ %>% slice_max(abs(M_mg_ind_skew_mean)) %>% select(M_mg_ind_skew_mean) %>% round(2)` (Figure 3, Table 2). Similarly, skew in fluxes towards high turnover taxa varied among streams ranging from `r pb_skew_summ %>% slice_min(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` to `r pb_skew_summ %>% slice_max(abs(pb_y_skew_mean)) %>% select(pb_y_skew_mean) %>% round(2)` (Figure 3, Table 2).

```{r trait hist, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
drake::loadd(spp_trait_histograms)
grid.draw(spp_trait_histograms)
```

The skew of energy fluxes towards populations with smaller/larger body sizes or higher/lower turnover showed weak, yet systematic variation with stream temperature (Figure 5). Skew towards larger body sizes was negatively associated with stream temperature. The mean effect size of increasing temperature was to shift the skewness coefficient, $Sk_{flux}$, `r M_skew_temp_coef_mean` units (`r M_skew_temp_coef_quant2.5` -- `r M_skew_temp_coef_quant97.5` 95% PI) for every 1 $^\circ$C increase. The estimated effect of temperature on $Sk_{flux}$ towards higher body size populations exhibited a bimodal distribution around zero (Figure SXa), but `r round((sum(M_skew_temp_coefs < 0)/n_boot)*100,1)`% of values fell below zero (Figure 4). Similarly, energy fluxes through the community skewed increasingly toward higher turnover (*P:B*)organisms with increasing temperature. The increase in $Sk_{flux}$ towards higher *P:B* populations was `r pb_skew_temp_coef_mean` (`r pb_skew_temp_coef_quant2.5` -- `r pb_skew_temp_coef_quant97.5` 95% PI; Figure 4).

```{r lorenz analysis, echo =FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, dpi = 450}
drake::loadd(lorenz_trait_fig)
grid.arrange(lorenz_trait_fig[["M_lorenz_flux_plot"]], lorenz_trait_fig[["pb_lorenz_flux_plot"]], ncol = 2, bottom = textGrob("Cumulative relative species", vjust = 1, gp = gpar(fontfamily = 'serif')),
                         left = textGrob("Cumulative relative flux", rot = 90, vjust = 1, gp = gpar(fontfamily = 'serif')))

@@

```{r skew statistics, echo=FALSE, warning=FALSE, message=FALSE}

```{r skew distribution, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="Figure 4. "}
drake::loadd(random_skew_fig)
grid.arrange(random_skew_fig[["M_perc_plot"]], random_skew_fig[["pb_perc_plot"]], ncol = 1, left = text_grob(""))

```{r skew prob temp, echo = FALSE, warning=FALSE, message=FALSE}
drake::loadd(temperature_skew_fig)
temperature_skew_fig
```
# Discussion

@@

[@diaz] SAD are more uneven than their statistical background

@@

We are grateful to Sigurður Guðjonsson, Guðni Guðbergsson, and the staff at the Veiðimlastofnun for providing laboratory space and logistical support. We are also grateful to Sveinbj€orn Steinþorsson at the University of Iceland for super-jeep transport to our field sites during the winter. Jeff Wesner and Abe Kanz for code sharing and discussions on modeling diet proportions.
